Capstone Movielens Report

### 2025-12-09 reports/capstone-movielens.site/05.appendix.Rmd
Temporary fix1.

Trains (and optionally *regularizes* if the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYDE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].

::: {.noteblock data-latex=""}
This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function (described below in section [UMGYDE Model: Regularization] of *this Appendix*) as shown in the [Usage](#func.regularize.train_UMGYD_effect.cv.usage) subsection of *This Function's Description Section* below.
:::

@@

::: {.noteblock data-latex=""}
In the above code snippet, the `regularize.train_UMGYD_effect.cv` function is called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function, along with the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (both described below in [UMGYDE Model: Regularization] section and this section, respectively).
:::
:::

@@

::: { #func.regularize.train_UMGYD_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

@@

The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).

::: {.noteblock data-latex=""}
:::
:::

@@

Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

>>>>

Trains and *regularizes* the *User+Movie+Genre+Year Effect (UMGYDE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].

@@

::: {.noteblock data-latex=""}
In the above code snippet, the `regularize.train_UMGYD_effect.cv` function is called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function described below, along with the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) function described above in this section.
:::
:::

@@

::: { #func.regularize.train_UMGYD_effect.cv.args.lambda .sidebar }
  - **lambda:** Regularization parameter $\lambda$.

@@

This is a helper function that is used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function described below in this section as shown in the [Usage](#func.regularize.train_UMGYD_effect.cv.usage) section of *this Description* above.

Under the hood, it calls internally the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).

::: {.noteblock data-latex=""}
For the *regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) to be correctly applied to the model being trained, the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument must be greater than zero (when the $\lambda$ is $0$ the *regularization* is disabled).
:::
:::

@@

Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::
